Analyzing Sakura Flowering Trends Under Climate Change

### 2024-12-03 paper/paper.qmd
add

```{r}
#| label: fig-flowering-distribution
#| fig-cap: "Distribution of Sakura Flowering Dates"
#| warning: false 
#| message: false
#| fig-align: center

@@

plot_flowering_distribution
```
```{r}
#| label: fig-temperature-distribution
#| fig-cap: "Distribution of Average Temperatures in March"
#| warning: false 
#| message: false
#| fig-align: center

@@

```{r}
#| label: fig-flowering-trend
#| fig-cap: "Trend of Sakura Flowering Dates Over Time"
#| warning: false 
#| message: false
#| fig-align: center

@@

```{r}
#| label: fig-temperature-trend
#| fig-cap: "Trend of Average Temperatures Over Time"
#| warning: false 
#| message: false
#| fig-align: center
#| 
plot_temperature_trend <- ggplot(clean_sakura_data, aes(x = year, y = avg_temperature)) +
  geom_point(alpha = 0.5, color = "darkorange") +
  geom_smooth(method = "loess", color = "red", se = TRUE) +
  labs(
    title = "Trend of Average Temperatures Over Time",
    x = "Year",
    y = "Average Temperature (°C)"
  ) +
  theme_minimal()
plot_temperature_trend

@@

```{r}
#| label: fig-flowering-source
#| fig-cap: "Comparison of Flowering Dates by Data Source"
#| warning: false 
#| message: false
#| fig-align: center

>>>>

```{r}
#| label: fig-flowering-distribution
#| fig-cap: "Distribution of Sakura Flowering Dates"
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center

@@

plot_flowering_distribution
```
```{r}
#| label: fig-temperature-distribution
#| fig-cap: "Distribution of Average Temperatures in March"
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center

@@

```{r}
#| label: fig-flowering-trend
#| fig-cap: "Trend of Sakura Flowering Dates Over Time"
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center

@@

```{r}
#| label: fig-temperature-trend
#| fig-cap: "Trend of Average Temperatures Over Time"
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center

plot_temperature_trend <- ggplot(clean_sakura_data, aes(x = year, y = avg_temperature)) +
  geom_point(alpha = 0.5, color = "darkorange") +
  geom_smooth(method = "loess", color = "red", se = TRUE) +
  labs(
    title = "Trend of Average Temperatures Over Time",
    x = "Year",
    y = "Average Temperature (°C)"
  ) +
  theme_minimal()
plot_temperature_trend

@@

```{r}
#| label: fig-flowering-source
#| fig-cap: "Comparison of Flowering Dates by Data Source"
#| echo: false
#| warning: false 
#| message: false
#| fig-align: center
